VOI-aware MCTS

### 2012-06-10 paper/vago.ecai/case-for-support.tex
fixes

The paper addresses an important issue of simple regret minimization
in Monte Carlo sampling in trees, and presenting the paper at the
conference and getting feedback from other researchers,
as well as attending other presentations in this and other fields of
AI is important for my ongoing studies in AI. However, travel,
logding, and registration costs are high, and without financial 
support I will have difficulty attending the conference.

>>>>

The paper addresses an important issue of simple regret minimization
in Monte Carlo sampling in trees, and presenting the paper at the
conference and getting feedback from other researchers,
as well as attending other presentations in this and other fields of
AI is important for my studies in AI. However, travel,
lodging, and registration costs are high, and without financial 
support I will have difficulty attending the conference.
